The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-03-12 src/ms.tex
add Gemini ack

We would like to thank the members of the community that have contributed to
\astropy, that have opened issues and provided feedback, and have supported the
project in a number of different ways.

@@

Furthermore, the \astropy packages would not exist in their current form without
a number of web services for code hosting, continuous integration, and
documentation; in particular, \astropy heavily relies on GitHub, Travis CI,
Appveyor, CircleCI, and Read the Docs.

>>>>

We would like to thank the members of the community who have contributed to
\astropy, who have opened issues and provided feedback, and have supported the
project in a number of different ways.

@@

Supported by the international Gemini Observatory, a program of NSF's NOIRLab,
which is managed by the Association of Universities for Research in Astronomy
(AURA) under a cooperative agreement with the National Science Foundation, on
behalf of the Gemini partnership of Argentina, Brazil, Canada, Chile, the
Republic of Korea, and the United States of America.

Furthermore, the \astropy packages would not exist in their current form without
a number of web services for code hosting, continuous integration, and
documentation; in particular, \astropy heavily relies on GitHub, Azure
Pipelines, CircleCI, and Read the Docs.
